Evaluating Public Health Standards in Toronto: An Analysis of BodySafe Inspection Data

### 2024-01-24 output/paper.rmd
work

---
title: "Exploring Urban Housing Dynamics: Challenges and Strategies in Toronto's Affordable and Social Housing Landscape"
author: 
  - Ziyi Liu
thanks: "Code and data are available at: https://github.com/liuziy23/Ziyi-Liu.git"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper delves into the multifaceted urban landscape of Toronto, focusing on the challenges and strategic responses linked with affordable and social housing.Toronto is one of the most populus and diverse cities in North America, it acts as a unique case study to examine urban housing dynamics. This research emoloys several dataset that include aspects such as affordable housing development, social housing waitlists and rental unit redevelopment. These findings reveal a complex housing landscape. The paper concludes with strategic recommendations for policy makers."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: reference.bib
---

@@

In exploring urban housing dynamics, we delve into the housing issues as reflected in the diverse datasets of Toronto's housing sector. This paper focuses in Toronto where it grappling with diverse housing challenges exacerbated by rapid urbanization and demographic shifts. With the data of rental housing transformation, affordable housing development, and the dynamics of social housing waitlists, this paper presents an analytical narrative on Toronto's evolving housing landscape. It examines how the city's policies and initiatives respond to the pressing needs for affordable and social housing, and discovering the challenges posed by urban growth, demographic changes, and economic pressures.

>>>>

---
title: "Evaluating Public Health Standards in Toronto: An Analysis of BodySafe Inspection Data"
author: 
  - Ziyi Liu
thanks: "Code and data are available at: https://github.com/liuziy23/Ziyi-Liu.git"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This study presents a comprehensive analysis of public health inspection data from Toronto's BodySafe program, aiming to evaluate the safety standards to personal service in the city. We examine the trends in public health standards including spas, salons and tatto parlors. We focuses on infraction categories, inspection outcomes, and the impact of enforcement actions. By investigating the correlation between service types, inspection results, and geographic distribution, this study provides insights of effectiveness of public health policies and the implementation. This paper not onlt focus on the effectiveness of BodySafe program but also investigating potential opportunities to enhance public health safety."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: reference.bib
---

@@
